Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2017-01-06 writing/DraftExposurePaper/DraftExposurePaper.Rmd

```{r echo = FALSE}
studies <- c("Czajkowski 2010", "Rezempour 2014", "Zandbergen 2009", 
             "Currie 2013", "Grabich 2016", "Zaharan 2010", "Kruk 2010", 
             "Villarini 2011", "Atallah 2007")
distance_km <- c("120", "", "Buffer", "25, 30, 60, 75", "30, 60, 100", 
                 "2 counties", "Radial Max Wind", "100-500", "")
rain_mm <- c("", "2/hr, 48/d", "", "", "", "", "", "", "200-500 (Floyd)")
wind_kt <- c("", "", "SSWS", "", "SSWS", "", "34, 50, 64", "", "")
exposure_parameters <- data.frame(studies, distance_km, rain_mm, wind_kt)
kable(exposure_parameters, "markdown")
```

>>>>

```{r echo = FALSE}
studies <- c("Davidson 2001", "Atallah 2007", "Kinney 2008", "Zandbergen 2009", "Czajkowski 2010", 
             "Zaharan 2010", "Kruk 2010", "Villarini 2011", "Rezempour 2014", "Currie 2013", "Grabich 2015", 
             "Grabich 2016")
distance_km <- c("Hurricane Disaster Risk Index (HDRI)", "", "County Center", "30 Buffer and Decay", "120", 
                 "2 counties", "Radial Max Wind", "100-500", "", "25, 30, 60, 75", "60", "30, 60, 100")
rain_mm <- c("HDRI", "200-500 (Floyd)", "", "", "", "", "", "", "2/hr, 48/d", "", "", "")
wind_kt <- c("HDRI", "", "", "SSWS", "", "", "34, 50, 64", "", "", "", "64", "SSWS")
exposure_parameters <- data.frame(studies, distance_km, rain_mm, wind_kt)
kable(exposure_parameters, "markdown")
```
